\chapter{Operations}

\section{Deposit process}
The deposit process consists of the user sending tokens into the
deposit wallet, and then the system moving tokens from the deposit
wallet into the accumulator wallet.  The trading system will generate
the keys of the deposit wallets, and these keys are stored encrypted
in the database.

The private keys of the accumultator wallet are available only with
the a senior manager, and should not be stored on the trading
platform.  Copies of the private keys of the accumulator should be
stored split in two and stored in the archvial location.

\section{Withdrawal process}

The withdrawal process consists of several steps.
\begin{itemize}
  \item Funds are moved from the cold wallets to the hot wallets and
    made available for withdrawal.  Typically this transfer should be
    made once per day and should consist of 120 percent of the average
    expected delay withdrawal volume.
  \item Withdrawals are approved by a staff member
  \item Withdrawals are then queued by the hot wallet and approve by a manager
\end{itemize}

\section{Asset Custody}
\subsection{Monitoring}

The following daily reports should be compiled and made available to
the customer advocate.


\section{Account acceptance}
\subsection{KYC}
\section{Suspicous activity procedure}
\section{Market surveillance}

\section{Client greivance process}
\section{Wallet management}
All wallets should be inventoried and each wallet should be desginated
as a business wallet, a client funds wallet.

All business wallets and client funds wallets should be held on
separate devices.  All devices with client wallets should contain only
corporate information.

\subsection{Business operations wallet}

* A wallet for business operations can contain up to 250k HKD using a
software device in the form of a mobile device.  This mobile device is
the property of the company and should not contain any


\subsection{Hot wallets containing client funds}

\subsection{Cold wallets containing client funds}


\section{Insurance}

Need to get price quotes for D&O and liability insurance
