\chapter{Operations}

\section{General}
The firm will use open-source software for all of its operations.  The
trading system used will be OpenCEX which is an open-source system
based on Python and Django.

\section{Electronic trading systems}
\crossref{Questionaire: VA-2: Section 1 Attachment business profile}
Our exchange will conduct electronic trading services according to the
following diagram
\begin{figure}
  \begin{adjustbox}{center}
\begin{tikzpicture}
  % Left boxes
  \node[draw, rectangle] (topLeft) at (0,0) {Traders};
  \node[draw, rectangle, below=2cm of topLeft] (bottomLeft)
       {\shortstack{External\\arbitrage trader\\(human or Hummingbot)}};

  % Right boxes
  \node[draw, rectangle,  right=3cm of topLeft] (topRight) {\shortstack{Our
    exchange\\trading engine}};
  \node[draw, rectangle, below=2cm of topRight] (bottomRight) {\shortstack{Other centralized and\\decentralized exchanges}};

  % Arrows
  \draw[->] (topLeft) -- (topRight);
  \draw[->] (bottomLeft) -- (topRight);
  \draw[->] (bottomLeft) -- (bottomRight);
\end{tikzpicture}
\end{adjustbox}
\caption{Schematic of the electronic trading system.}
\end{figure}

The exchange itself will not forward or route orders from the trading
engine, but will rely on external market makers or bots controlled by
external market makers to ensure that the exchange maintains in
equilibrium with other markets.  These external market makers or bots
will be trading with their capital, with their virtual assets
subject to custody as client funds by the exchange.

As with other virtual assets, acceptance, execution, clearing, and
settlement are integrated into one process on the exchange.

\subsection{Access to trading platform}
\crossref{VA-1: Question 35(a)-(b)}
The firm allows access to our OpenCEX trading platform through internet
browsers and a token-based application programming interface which
allows for trading only through an API key. We intend to make the
OpenCEX platform tradable through the Hummingbot bot trading platform.

The trading platform uses a thick client browser model by which the
internet browser runs a Vue.js application that can send commands to
the trading backend through a web sockets API, although the browser
based API is subject to change and is intended for only server-client
communications through our frontend.  The protocols between the browser
and the client are documented for testing purposes, but we do not
guarantee the stability of calls not officially documented as part of
our API.

Overseas investors can access our trading platform.  Client onboarding
is based on our AML/KYC policies, and there are no specific
restrictions on overseas clients.

\subsection{Market making / liquidity provision}
\crossref{VA-1: Question 37(d)}
All market makers and liquidity provisions will be made by clients
placing orders directly on the trading system, placing orders into the trading
engine.  Any market makers will be vetted with the same onboarding
requirements as other clients.  The market makers and liquidity
providers will trade on the same conditions as other clients, but may
receive fee discounts and rebates on the same terms as other clients.

\section{Custody of Virtual Assets and Fiat Assets}
\crossref{Appendix F1: Part C}
\crossref{VA-1: Question 82}
\crossref{VA-1: Question 92}

There are three types of wallets:
\begin{itemize}
  \item trading wallets — The keys for these are generated by the
    trading system and these are wallets for which the trading system
    has access,
  \item custody wallets – These wallets are stored in multi-signature
    shared wallets with signature devices.  All custody wallets are
    offline and will be set up so that there isn't a private key
    available for the wallet itself, and all signatures are made with
    hardware digital chops to authorize fund movement,
  \item business operation wallets – These wallets are used internally
    for business operations and are separate from the wallets used for
    custody
\end{itemize}

The keys for all wallets are generated via hardware devices without
manual intervention using hardware random sources. 

\subsection{Client fund segregation}
\crossref{VA-1: Question 95}
\begin{itemize}
\item REMEMBER, IT IS NOT YOUR MONEY.  IT IS NOT THE FIRM'S MONEY.  IT IS THE CLIENT'S MONEY.
\end{itemize}

All client funds will be segregated into separate wallets and bank
accounts, which are to be under the legal ownership of the associated
entity, and will not be subject to claims against the parent entity.
The associated entity will have a one-way liability guarantee by
which losses in the associated entity will be guaranteed by the parent
entity, but any liabilities of the parent entity will not be assumable
against the associate entity.

\begin{itemize}
  \item All client assets are to be stored in separate wallets from
    business operations wallets.
  \item No staff is allowed to have direct access to the private keys
    of either hot
    wallets or cold wallets.  Hot wallets are to be managed by the
    trading system, while cold wallets are to be managed via
    tamperproof hardware devices 
  \item All wallets should be inventoried and each wallet should be designated
    as a business wallet, a client fund wallet.
  \item All business wallets and client fund wallets should be held on
separate devices.  All devices with client wallets should contain only
corporate information.
\end{itemize}

\subsection{The custody lifecycle}
\crossref{VA-1: Question 89}
\crossref{VA-1: Question 88}
The flow of client funds is illustrated in Figure \ref{fig:lifecycle}.  Funds from the
client will go into a client deposit wallet, which is generated by the
trading system.  Funds from the client deposit wallet are
automatically swept into the cold storage accumulator wallet by the trading
system.  The funds from the cold storage accumulator wallet are then
processed by the custody team into internal wallets under the control
of the custody team.

When a withdrawal is processed, the custody team will manually move
assets from the cold storage wallets under their control into a
``keeper wallet''.  The keeper wallet is a hot wallet under the
control of the trading system.  After receiving the proper approvals
by the operations team, the trading system will process the withdrawals
from the hot keeper wallet. 

The hot wallets are generated by the trading system and are managed by
the technology department, with access available only through the
trading system by operations staff.  No staff will have direct access
to the hot wallets.  The operations staff will interact only with the
hot wallets through the trading system.  The technical staff will not
normally have direct access to the hot wallets.  Although technical
staff may access the wallets through reverse engineering the trading
system, direct access to the trading system database will be limited
to a few technology staff, and operational processes will
prevent a member of the technology staff from having sufficient access
to the trading system to reverse engineer the private keys of the
hot wallets.

The cold wallets managed by the custody department, and all cold
hardware wallets, will require physical hardware devices and no less
than two signatures to move the wallets.  The cold storage wallets
will be ``air gapped'' and will not be electronically connected to any
other system.

Any business operations wallets are managed by the finance
department.  No client money will be transferred to the business
operations wallets.

All client assets are moved to cold wallets as quickly as possible,
and the amount in the "keeper" withdrawal wallet is limited to
amounts that are subject to immediate withdrawal by the trading
system.  Under normal circumstances, the exchange will not have more
than 2 percent of its assets in the keeper hot wallet.  Normally,
funds will be transferred from cold storage to hot storage periodically
through the day to ensure that any withdrawals can be
promptly processed by the trading system.

The keeper withdrawal wallet is password protected and will require a
signature from a senior operation manager to access funds.

\begin{figure}
  \label{fig:lifecycle}
\begin{adjustbox}{center}
\begin{tikzpicture}[node distance=1.5cm, every node/.style={draw, minimum width=1.5cm, minimum height=1cm}]

% Blocks
\node (externaldeposit) {\shortstack{External\\wallet}};
\node[right=2cm of externaldeposit] (block1) {\shortstack{Client\\Deposit\\Wallet}};
\node[right=3cm of block1] (block2) {\shortstack{Accumulator\\Wallet}};
\node[below right=1cm and 3cm of block2] (block3) {\shortstack{Internal\\vault\\wallets}};
\node[below=3cm of block1] (block4) {\shortstack{Keeper\\wallet}};
\node[below=3cm of externaldeposit] (block5) {\shortstack{External\\withdrawal\\wallet}};

% Arrows
\draw[->] (externaldeposit) -- (block1);
\draw[->] (block1) -- node[midway, above, draw=none] {\shortstack{Automatic\\sweep}} (block2);
\draw[->] (block2) -- (block3);
\draw[->] (block3) -- node[midway, above, draw=none] {\shortstack{Manual\\transfer\\by\\custody}} (block4);
\draw[->] (block4) -- node[midway, above, draw=none] {\shortstack{Subject\\to\\operations\\approval}} (block5);

% Dotted box
\node[draw, dotted, fit=(externaldeposit)(block5), inner sep=0.5cm, label=above:{User wallets}] {};
\node[draw, dotted, fit=(block1)(block4), inner sep=0.5cm, label=above:{\shortstack{Hot wallets\\in trading system}}] {};
\node[draw, dotted, fit=(block2)(block3), inner sep=0.5cm, label=above:{\shortstack{Cold hardware\\wallets\\held by custody}}] {};
\

\end{tikzpicture}
\end{adjustbox}
\caption{Wallet structure}
\end{figure}

\subsection{Transfer from client wallet to house wallet}
\crossref{VA-1: Question 87}
Fees from trading and withdrawals in the trading system will be
credited to a "fee user" in the trading system that will be under
the control of a user created by the exchange.  The fee user will
periodically withdraw the amount to the business operation wallet,
and this withdrawal will be processed by the operations and custody
staff as a withdrawal by any other user.

\subsection{Design and operation of the custody function}
\crossref{VA-1: Question 83}

The trading system consists of open-source developers, and the custody
function was created by a team of developers who are working on the
OpenCEX system.  There is a private informal study group consisting of
potential Hong Kong VASP licence applicants on telegram which
developed the custody system to work with the OpenCEX system. This
study group came up with a set of best practice standards for
licensees.

The operation of the custody function will be as described in the
chapter on governance and staffing.

\subsection{Access to wallets and keys}
\crossref{VA-1: Question 85}
\crossref{VA-1: Question 86}

All custody wallets are physical hardware devices that are in the
possession of a single user and which require authentication and
physical access by the user to use the device.  The hot wallets
in the trading system may only be accessed by the operations staff
through the trading system, and operations staff do not have direct
access to the wallets.

Access to the hot wallets is possible through reverse engineering the
transaction database of the trading system, but this access will be
highly restricted to a few technology staff people.

\subsection{Amounts kept in hot/cold wallets}
\crossref{VA-1: Question 89}
We will minimize the number of virtual assets kept in hot wallets, and
we expect that only 2 percent of virtual assets will be kept in hot
wallets.  The custody function will have access to the quantity of
virtual assets in both hot and cold wallets and as transfers from cold
wallets to hot wallets are a process that will require manual
intervention and multiple signatures, any policy limits on amounts
held in hot and cold wallets can be manually enforced.

\subsection{Hot wallet management}
\crossref{VA-1: Question 90}
\status{Fully implemented}
Our trading system OpenCEX maintains only two sets of hot
wallets.  User deposit wallets and the keeper withdrawal wallet.
Funds that are deposited into the user deposit wallets are immediately
swept into the cold storage accumulator wallet.

There is another password-protected hot wallet which is used by the
OpenCEX to process withdrawals.  The seed and keys for this wallet are
generated internally by the OpenCEX system using entropy, which is
generated by the system using the hardware "urandom" device.  The
keys for the keeper wallet are not normally made available to staff
but could be accessed via administrative access by technical staff.

To prevent unauthorized access to the hot wallet keys, the
operations staff do not have access to the technical infrastructure
and the technical staff do not have access to the withdrawal functions
of the system.

The keys for the hot wallets are stored within the trading system.
This makes it possible for the technology staff to pull the keys from
the hot wallets, and access to the trading system should be
minimized for the technology staff and forbidden by the operations
staff.  The keys from the hot wallets are available through database
backups and therefore database backups should be kept in a secure
encrypted format.

\subsection{Hot wallet testing}
\crossref{VA-1: Question 91}
\status{Fully implemented}
The hot wallets are under the control of the OpenCEX trading system
which is run in the virtual environment, and we maintain a separate
instance of the trading system and run regression tests against the
system to ensure the reliability of the hot wallet.


\subsection{Client internal segregation}
\crossref{VA-1: Question 97}
\status{Fully implemented}
Generally speaking, client virtual assets will be pooled with other
assets.  Clients will have individual "hot wallets" for deposit, but
the contents of those wallets will be swept into cold storage.

\subsection{Custody wallet standards}
\crossref{Appendix F1: Part C(ii)-(iii)}
\periodic{Semiannually - Custody - Test hardware wallet backups}

All custody wallets are to be cold wallets, which will be shared and
will require at least two signatures from hardware devices.

There will be three backup signature devices.  One will be stored in the law office, another in the accounting office and the third in a
safe deposit box in a bank.  All backup signature devices will be
physically present in Hong Kong and will be subject to legal processes
by regulators and the Hong Kong authorities.  Backup signature devices
are to be tested semi-annually but are not to be otherwise used except
in cases of emergency.  The three backup signature devices should be
from different hardware vendors.

Each custody signature device will be used only for custody purposes.
The head of the departments will be issued their signature
devices.  Any signature devices that are to be shared between staff
may be used only on the premises of the main offices and are under no
circumstances allowed to leave the main office.

Signature devices are not to be used for any purposes other than to
sign custody wallets.  The custody department may divide custody funds
into a set of wallets to ensure that no one wallet contains all the
funds and to ensure that access to the custody wallets is divided
between the custody staff.

\begin{itemize}
  \item Custody wallets are never to be put online and are never to be
    accessed through any means besides hardware devices.
  \item All custody wallets will be accessed via hardware storage
    modules that have been certified at a security rating of
    FIPS-140 Level III.  The custody signature devices should be
    accessed through several vendors.
 \item The keys and wallet addresses are to be generated directly from
   the hardware storage module.
 \item A signature for custody will require physical possession
   of the hardware device
 \item The hardware devices are to be kept in the main location of the
   firm and all actions involving cold storage will take place within
   the physical location of the business.  The cold storage hardware
   devices are not to leave the physical location of the business, and
   when not in use they will be kept in a safe in the firm.
 \item Each hardware device used in business operations will be
   password protected by a password known only to the user of that
   device.
\end{itemize}

Before any custody wallet is used, it is to be tested by pushing a
a small quantity of coins through the wallet to ensure that the coins can
only be released with the signature device.

\subsection{Auditing of wallet contents}
\crossref{Appendix F1: Part C (vi)}
\crossref{VA-1: Question 94}

Reconciliation will be done daily, in which the contents of
all wallets are to be audited to ensure that no transactions are
unaccounted for.

We will develop software that will provide instantaneous alerts and
warnings for unauthorized and unexplained transactions.

\subsection{Communications policy}
\crossref{VA-1: Question 93}
In the event we detect fraudulent activity, our primary goal will be to
safeguard client assets and ensure that forensic information is kept.
We will activate our cybersecurity contingency plan to safeguard
assets and then activate our incident reporting system to ensure that
law enforcement and the SFC are notified of the incident.

Once we have assessed the situation and can provide
information to the public, we will communicate the issue and the
situation through our social media channels.

\subsection{Business operations wallets}

Wallets that are used for business operations are to be kept
completely separate from those which are used by custody.  The amounts
and access to business operation wallets are to be decided by the
managing director.  The signature devices used for business operation
wallets are to be separate from those used by the custody function.

\subsection{Deposit process}
\crossref{VA-1: Question 76}
The deposit process consists of the user sending tokens into the
deposit wallet, which the system then moves tokens from the deposit
wallet into the accumulator wallet.  The trading system will generate
the keys of the deposit wallets, and these keys are then stored encrypted
in the database.

\subsection{Withdrawal process}
\crossref{VA-1: Question 76}
The withdrawal process consists of several steps.
\begin{itemize}
  \item Funds are moved from the cold wallets to the hot wallets and
    made available for withdrawal.  Typically, this transfer should be
    made once per day and should consist of 120 percent of the average
    expected delay withdrawal volume.
  \item Withdrawals are approved by a staff member.
  \item Withdrawals are then queued by the hot wallet and approved by a manager
\end{itemize}

\subsection{Third-party fund deposits and withdrawals}
\crossref{VA-1: Question 75}
\status{Fully implemented}
We do not allow for third-party withdrawals or third-party fiat
deposits unless the account holder is a licensed finance intermediary.
We will to the best of our ability monitor deposit patterns to ensure
that the deposit patterns of virtual assets are consistent with the
information provided by the client.

\subsection{Digital wallet ownership of client}
\crossref{VA-1: Question 77}
\status{Fully implemented}
We believe that it is technologically impossible to insure ownership
of wallets, and the most that can be done is to use our anti-fraud /
CFT measures to ensure that the use of the system is consistent with
the KYC information provided by the client.

\subsection{Suspension of deposits and withdrawals}
\crossref{VA-1: Question 78}
\status{Fully implemented}
We note that there is no technological process by which we can suspend
deposits to our wallets.  The most that can be done is to not
credit deposits to client accounts and not make virtual assets
available for trading.

We will suspend withdrawals and stop crediting a user account under
the following situations:
\begin{itemize}
\item If we believe that the system as a whole has been compromised
\item If we believe that a user account is being used for purposes
  inconsistent with the documentation provided by the client
\item If we believe that the account is being used for money
  laundering or fraudulent activities
\item If we have received binding legal instructions (such as a court order)
\end{itemize}

In cases where there is a general outage, the users will be informed
through our telegram site and the SFC will be informed through
standard escalation channels.

In cases, where there is a specific outage, we will handle those
situations on a case-by-case basis.

\subsection{Deposit and withdrawal limits}
\crossref{VA-1: Question 79}
\status{Fully implemented}
Deposit and withdrawal limits are set by the chief operations officer,
and are set based on the ability of the company to handle a given
quantity of deposits and withdrawals.

\subsection{Fraudulent client transaction requests}
\crossref{VA-1: Questions 93 and 94}
Currently, all withdrawals are manually vetted and require the approval
of three staff members.  One to fund the hot wallet.  One to approve
the request and one to approve the withdrawal.

In the case of possible fraud, we will contact the account holder or the
designated representative of the account holder.  We will also collect
all necessary forensic information and contact the Hong Kong Police as
necessary.


\ifthenelse{\boolean{bankless}}{
\section{Cash and token management for bank-less exchanges}

\subsection{No cash deposits by clients}
The exchange will not hold any cash from clients or accept any cash
deposits.  All paper fiat held by the company is intended for
internal business purposes only.

\subsection{Paper cash must be physically separated}
All paper cash held by the firm must be held in a secure location and
kept strictly separate from other cash, particularly any personal cash
held by staff.  All deposits and withdrawals of cash from the firm
must be recorded in the ledger.

The company will maintain an inventory of all locations in which firm
cash is being kept and will ensure adequate security standards.
See physical infrastructure.
}{
  \subsection{Fiat deposit and withdrawal}
  \crossref{VA-1: Question 73}
Our trading platform does not handle fiat/virtual asset trades, so a
fiat deposit will be made through an OTC transaction by which a client
deposits or withdrawals fiat currency to the firm at which point the
firm will perform an OTC transaction to sell or purchase virtual assets
with the client and then deliver the assets to the exchange
platform if requested by the client.

Any fiat that is held on behalf of a client will be held in a separate
bank account opened under the name of the associated entity.  However,
due to bank requirements, we will not be able to undertake fiat
custody until we have received clearance to do so from our bank and
until we have added fiat trading into the exchange.  Until this occurs
we will perform an OTC transaction with fiat currency to convert to
virtual assets for trading on the exchange.

\subsection{Deposit and withdrawal channels}
  \crossref{VA-1: Question 74}

We will accept bank transfers to our bank account or paper cash
deposits made directly to our place of business.  Any fiat deposits
and withdrawals will be converted immediately to virtual assets in an
OTC trade and sent to the address requested by the client.

In the event that the fiat cash is intended for exchange trading, we
will require that the account on the exchange matches the identity of
the client and we will perform AML/KYC required by
SFC guidelines, including but not limited to ID verification, if the OTC transaction is intended to onboard funds onto the exchange.

\subsection{Fiat management}
\crossref{VA-1: Question 96}
It is our intention that client assets be held in a separate bank
account which is legally owned by the associated entity.  Until we are
able to acquire such an account, we will not hold fiat on behalf of
clients but instead use P2P and OTC transactions to immediately
convert client fiat into virtual assets to be managed under the
custody wallets.
}

\section{Know your clients (KYC)}
\crossref{VA-1: Question 36(b)}
\crossref{Appendix F1: Part D}

The types of accounts that we expect to open can be classified as:

\begin{itemize}
\item Retail accounts
\item Professional investors who are not financial intermediaries
\item Financial intermediaries
\item Staff trading accounts
  \end{itemize}

\subsection{Professional investors}
\crossref{VA-1: Question 17}
\crossref{VATP Guidelines: Schedule 1}
\status{Fully implemented}

We expect that most of our professional investor clients will be
licensed intermediaries or institutional professional investors, as
defined in Schedule 1 of the Securities Futures Ordinance.  In cases
where we are onboarding an institutional profession investor, we will
ask for a licensing certificate from the client and then verify the
certificate with the appropriate licensing body.  In cases where we
are dealing with a professional investor with a required capital
requirement, we will ask to see documentation as provided in section
8 of the Professional Investor Rules.

For internal policies, the licensed jurisdictions would include Hong
Kong, Singapore, Dubai, the United States, the United Kingdom, or the
European Union, and licences will include licences for brokerages,
money services, banking, insurance, and investment advisers.

In the case where we are dealing with a financial intermediary, our
policy will be to focus on due diligence in ensuring the identity of
the client and that they are, in fact, a licensed entity.

In cases where we are dealing with non-licensed entities, we will ask
for a bank statement or other proof of assets.  We expect that many of
our clients may have large assets in the form of virtual assets.  To
qualify as a professional investor, we may have a custodian, certified
public accountant or auditor examine the blockchain and provide a
certificate that an individual or corporation possesses the required
capital under the Professional Investor rules.

\subsection{Client knowledge}
\crossref{VA-1: Question 18 a, b, c, d}
\status{Fully implemented}

The firm wishes to focus on sophisticated investors (such as financial
intermediaries).  In cases where the entity is a licensed
financial intermediary, we will take the existence of a licence as
evidence that the client as sufficient knowledge of relevant risks.

We will not take on clients that have no knowledge of virtual assets.

In cases of retail investors, we will ask the individual about their
level of knowledge and only admit individuals who, we believe, are
aware of the risks of investing.  We will encourage unsophisticated
investors to go to other exchanges.

The reason this is viable for our firm involves our business model.
Our business model is focused not on retail investors, as these
investors require much hand-holding and customer support.  Rather, by
focusing on active developers and financial intermediaries, we
drastically reduce our customer support costs.

In the case of a client with no knowledge of virtual assets, we would deny
the account and provide references to other exchanges or industry
groups that could provide the necessary training.

\subsection{Financial losses}
\crossref{VA-1: Question 19}
\status{Fully implemented}

The clients on our exchange are focused on sophisticated clients who
are either financial intermediaries or technology sophisticated
developers who are actively in the cryptocurrency business.  We will
not accept accounts from individuals that we do not believe to be
sophisticated investors or who we believe to lack the necessary financial
resources.

\subsection{Client onboarding}
\crossref{VA-1: Question 20}
\status{Implementation in progress}

We are using the identity provider subsum to identify the identity of
the client.  For Hong Kong retail clients and financial
intermediaries, we will require that the client come to our office for
a face-to-face meeting, and we will check the licensing status of the
financial intermediary.

\subsection{Client identity}
\crossref{VA-1: Question 21}
We will ask the client to provide standard identity and KYC documents
and then use a third-party identity service (Subsum) to verify the
validity of these documents.  In situations where we are dealing with
a financial intermediary, we will require that a representative of the
financial intermediary located in Hong Kong physically meet with us in
our office, and we will verify the licensing status of the financial
intermediary with the licensing authority.

\subsection{Retail clients risk tolerance}
\crossref{VA-1: Question 22a, 22b}
\status{Questionaire to be developed}

For Hong Kong retail clients, we will ask that a retail investor fill
out a questionnaire and understand the risks and losses that are
possible with virtual assets.  In developing this questionnaire, we will
work with industry groups in Hong Kong to develop a standardized
questionnaire.

As part of our onboarding process, we will ask that all clients reveal
the name of a client reference for whom we can share client and
trading information with.  We expect that in most cases, the client
reference will be a close relative, and in cases where we believe that
the client is undergoing excessive losses we will contact the client
reference.

Generally speaking, we will not set risk limits for retail clients.  In
situations where we do not feel that the retail client has sufficient
knowledge to undertake the risks of virtual assets, we will not open
an account.  As part of our AML/KYC/Anti-Fraud measures, we will
monitor client accounts for trading losses, and if we find a client
with unusually large losses, we will investigate to seek appropriate
measures.

\subsection{Client identity address and contact details}
\crossref{VA-1: Question 23}
\status{Questionaire to be developed. Scheduled to be developed before
December 2023}
During our client onboarding process, we will ask the client for the
expected volume and types of trades and whether the client is a
financial intermediary.  In cases where the client is expected to have
a large volume of trades or a financial intermediary, we will arrange
for a face-to-face or video conference call.  We will ask that the
financial intermediary perform the call from their office and ask for the
intermediary to video the location of their office.  We will also make
on-site visits to the client office.

\subsection{Use of system and technologies testing}
\crossref{VA-1: Question 24}
We have not yet conducted testing of facial recognition and checking
of security features, but we intend to do spot-checking of these
features before becoming fully licensed.

\subsection{Non-face to face channel}
\crossref{VA-1: Question 25}
For non-face-to-face channels, we intend to make heavy use of video and
meetings to verify the identity of the
prospective client.  In particular, with accounts for financial
intermediaries, we will require a face-to-face meeting in the office of
the intermediary.

\subsection{Client master database entry}
\crossref{VA-1: Question 26}
We intend to keep client particulars offline with paper documents
stored in our main office.  Client particulars will not be kept online
and will not be available to trading and operations staff.

\subsection{Client review}
\crossref{VA-1: Question 27}
Each client will undergo a quarterly review in which we will examine
their trading record and identify whether their trading is
consistent with their stated activities.  We will also review each
client if unusual trading and withdrawal patterns are noted.

\subsection{Account opening documents}
\crossref{VA-1: Question 28}
We have not completed a draft of our account opening documentation, and
we expect to have those documents completed end of Quarter Three, 2023.

\subsection{Financial intermediaries}
\crossref{AML Guidelines: Section 4.8}

We consider licensed financial intermediaries including money services
operators, family offices, and licence brokers to be low-risk and
hence subject to simplified due diligence according to the criteria in
section 4.8 of the AML guidelines.  We expect that a
licensed financial intermediary would maintain adequate AML/KYC
protections to satisfy their regulators, and hence it would be
unnecessary for us to add another level of AML/KYC.

Our main concern regarding due diligence regarding financial
intermediaries is that they are who they say they are, and that they
the information that they provide is accurate.  In onboarding a
financial intermediary, the staff will check to see that the
intermediary is, in fact, licensed and that the person opening the
account is an authorized agent of the intermediary.  The staff will
monitor the intermediary with ongoing checks to make sure that there
has been no enforcement action taken.

\subsection{No cross-exchange, vostro, nostro accounts}
The company will not maintain an account with another exchange nor
allow another exchange to hold an account with the company, and will
not maintain nostro or vostro accounts.  Our main concern is that
cross exchange accounts will create "hidden leverage" in the
financial system and will cause leverage

\subsection{No third-party trading for non-FI accounts}
Individuals who are not financial intermediaries are not permitted to
trade on the exchange on behalf of third parties.

\subsection{Fund manager accounts}
\crossref{VA-1: Question 98}
Where a client is a fund manager, an account may be either opened in the name of
the fund manager or in the name of the funds, as determined by the
fund manager,

\section{Basic usage}
\subsection{Demonstration account}
\crossref{VA-1: Question 29}
Please refer to the appendix for a demonstration account.

\subsection{Technical specification}
\crossref{VA: Question  30a, b, c}
Our technical specification is available at
https://github.com/Polygant/OpenCEX-backend/tree/master/public\_api
and contains all order types.  The functional documentation does not
include fee structure.

Our technical specification document does not contain all messages,
requests, error codes, and status updates.  However, the source code
for our trading engine is open source and this information can be seen
from the source code of our trading engine.

We do have a simulation environment that allows for client
trading.  This simulation environment is made on request and is also
used for cybersecurity testing.

We plan to have a dedicated person for technical support and at least
one person available 24/7.  Our systems are open source, and we intend
to hire an outside vendor for the development of our trading systems in
addition to second and third-level support.

\subsection{Communications with clients}
\crossref{VA-1: Question 31}
\status{To be implemented by October 2023}
We will have a dedicated telegram channel set up to report on trading
suspension issue.

\subsection{Product information}
\crossref{VA-1: Question 32}
\crossref{VATP Guidelines: Schedule 2}
\status{To be implemented by October 2023}
Our website will contain a disclosure document on each virtual asset
available for trading, and will contain the general risk disclosure
as indicated by Schedule 2 of the VATP Guidelines.

\subsection{Statements}
\crossref{VA-1: Question 33}
Our exchange will not issue separate statements outside the information available from the exchange.

\subsection{Mobile devices}
All wallet and cash management will be done via mobile devices issued
by the company.  Staff are not to put wallet information on personal
devices.

\subsection{Login and authentication}
\crossref{VA-1: Questions 36, 36(a), 36(b)}
\crossref{VA-2: Question 2.5 (c)}
\crossref{Appendix F1: Part H(x)}
\status{Two factor authentication is optional but will be made mandatory}

We authenticate the identities of the users using two-factor
authentication using Google Authenticator or SMS verification.  To prevent spamming and bot logins, we use Google reCAPTCHA.

Our staff does not have access to password information, and password
information uses standard hashing protocols to ensure that a leak in
the database is resistant to direct attack.  The use of two-factor
authentication or SMS verification ensures that a password leak does
not allow an attacker either external or internal to gain immediate
access to an account.

Withdrawals will require e-mail/SMS verification and must be vetted by
internal staff.

System users will be authenticated through a system of two-factor
authentication with minimum password length and complexity, session
timeouts, and lockouts after invalid login attempts.

\section{Anti-money laundering / counter-financing of terrorism /
  anti-fraud (AML/CFT)}
\crossref{Appendix F1: Part E}

\subsection{General principles}
\crossref{VA-1: Questions 43, 44}
\status{To be implemented upon funding}

Our money laundering / anti-terrorist financing transactions
procedures are integrated into our anti-fraud transaction procedure,
and focuses on monitoring withdrawals to ensure that withdrawals are
not being used for illicit purposes.  All withdrawals are manually
vetted for anti-fraud measures, and we will develop code that will
flag suspicious transactions as our integrated anti-fraud measures.

Our AML/CFT/Anti-fraud activities will focus on examining and
carefully vetting client withdrawals.  The primary responsibility for
the AML/CFT/Anti-fraud activities will be made by the operations
staff.  The operations staff will be provided access on a "need to
know" basis on the activities expected by each client

Regarding deposits and withdrawals, our OpenCEX trading engine
is integrated with "Know your token" services such as Scorechain.
All deposit and withdrawal addresses will be processed through "know
your token" services.  If the service indicates that
the tokens being moved to or from a wallet which identified with fraud
or illicit activity, we will take appropriate action such as
delaying or blocking the transaction, filing a suspicious activity
report, or contacting the appropriate authorities.

\crossref{VA-1: Question 45}

\subsection{Red flags}
\crossref{VA-1: Question 46}
\status{Fully implemented}

* Client, or the client’s beneficial owner, being a politically exposed person or the business relationship assessed is of high risk

In situations where we are dealing with a non-financial intermediary
(i.e., a family office) we will identify the beneficial owner and
monitor the account closely for signs of illicit activity.  However,
we would prefer to avoid duplication of resources and wish to maximize
client privacy, and in these situations we would advise the client to
work with a licensed broker or fund who would perform the necessary
AML/KYC and client vetting and to have the financial intermediary
route orders through the exchange.

Regarding politically exposed persons, we are particularly
sensitive to anti-corruption efforts in Mainland China and the use of
virtual assets to fund activities that are prejudicial to the
national security of the People's Republic of China.  In cases where
we believe there to be a national security or anti-corruption risk, we
shall immediately inform the appropriate enforcement authorities.  We
will work only with financial intermediaries who, we believe, have
similar policies and will not act against the national interests of
the People's Republic of China or against the laws of the Hong Kong
Special Administrative Region.

* Use of proxies, any unverifiable or high-risk geographical location,
disposable email address or mobile number, or use of a constantly
changing device to conduct transactions by the client.

We will strictly enforce Hong Kong laws such as the United Nations
Sanctions Ordinance and immediately inform law and regulatory
enforcement if we have any belief that VPN's and proxies are being
used to circumvent the laws of Hong Kong.  Furthermore, we will freeze
accounts if we believe that the VPN is being used by persons within
Hong Kong to circumvent SFC regulation.

However, are against the concept of "high-risk geographical
locations" as many locations labelled "high risk" are in fact areas
which underserved financial infrastructures for which it is in the
interests of Hong Kong and the People's Republic of China to increase
business with.

Furthermore, there are legitimate uses for proxies.  For example, the
United States government has blocked certain websites such as labour
and census statistics from use by Hong Kong users, and a trading bot
that accesses this data must use a proxy.  Most companies require
internal users to route their internet usage through proxies for
compliance reasons, and may randomize or hide IP addresses for security
purposes.  Where we have identified a legitimate use or explanation
for the activity, we will allow that activity to continue, and will
work with regulators and industry groups to distinguish between
legitimate and illegitimate uses of these tools.

* Client transactions involving tainted wallet addresses, such as
“dark net” marketplace transactions or tumblers

We will match deposit and withdrawal wallets against public lists of
tainted wallet addresses.  In cases where we suspect illicit activity,
we will file suspicious activity reports with the proper
authorities.

We will be especially careful with withdrawals to tainted wallets.  In
case an account is being used to withdraw virtual assets to a
tainted wallet, we will look at the pattern of withdrawals to see
whether the account holder is the perpetrator of illicit
activity or a potential victim, and we will take appropriate action.

* Client transactions involving virtual assets with a higher risk or
greater anonymity (for example, virtual assets which mask users’
identities or transaction details)

We do not and have no plans to exchange or trade virtual assets with
high levels of anonymity.  All the virtual assets that we currently
trade and intend to trade are those whose transactions are publicly
available on the blockchain.

* Client transactions that are complex, unusually large in amount or
of unusual pattern, or have no apparent economic or lawful purpose

We will examine the underlying motivation behind these transactions
and take appropriate actions based on whether the underlying
motivation is consistent or opposed to the national interests of the
People's Republic of China and the laws of the Hong Kong Special
Administrative Region.  In situations where we conclude that the
underlying activity promotes activities that are contrary to the laws
of the HKSAR and the national interests of the People's Republic
of China or if we are unable to determine the ultimate purpose of
these activities, we shall work with the authorities to address them with
these activities according to law.

\section{Trading and settlement}
\subsection{Pre-trade risk management}
\crossref{VA-2: Question 2.11(a)}
\status{Fully implemented}
The system shall be set up to prevent the entry of any orders that exceed
trading and credit limits, alerts users to potentially erroneous orders
and prevents entry of erroneous orders, and prevents entry of orders
that are not in compliance with regulatory requirements.

\subsection{Order books arrangement}
\crossref{VA-1: Question 37(a)-(c), 37(e)}
\status{Fully implemented}

Our exchange operations consist of continuous trading through a dual
auction arrangement.  Any off-platform trading will consist of
fiat/OTC transactions that are independent of the trading platform.
The exchange engine will do no order routing, and any interaction with
other exchanges will be done by off-platform trading by clients acting
on their accounts.  The exchange will not access the order books of other
exchanges.

As a courtesy, we will provide information about the market prices of
the assets on an informational basis.  These quotes will not be used
for trading.  The quotes we will prove initially will be virtual asset
to virtual asset quotes.

We will offer only limit orders and stop-limit orders.  The stop-limit
order will be processed in the order executed by the system.  We do
not support hidden orders or iceberg orders or any other types of orders.

Any market-making or liquidity provision will be done by clients
placing orders on the exchange.  We will not access the order books of
other exchanges to determine prices, and we will not route orders to
other exchanges through our trading system.

The OpenCEX platform has a server-client model by which executed
trades are distributed to clients via an API.  The audit trail is
maintained in the records of the trading system, and we will make
provision to periodically dump the records of the trading system for
archival purposes.

Our trading order is a simple matching mechanism that does not have a
price/time priority algorithms.


\subsection{Trade confirmation and post-trade settlement}
\crossref{VA-1: Question 40}
\status{Fully implemented}

Trade confirmations will be performed by sending an e-mail to the account holder.  Trades will settle immediately and there will be no
process necessary for post-trade settlement.

\subsubsection{Off-platform trading arrangements}
\crossref{VA-1: Question 39 a,b}
\status{Fully implemented}
The exchange will require that customers enter orders directly into
the trading system, and will conduct exchange operations outside
the platform.

The exchange may conduct OTC trades of virtual assets in exchange for
fiat currency.  These transactions will be completely separate from
the activities on the exchange platforms.  Any OTC trades for virtual
assets will generally be an immediate swap between funds
and virtual assets.  The exchange will not use client wallets or
client-deposited funds for OTC purposes.

\subsubsection{No telephone instructions}
\crossref{VA-1: Question 38}
\status{Fully implemented}
The exchange will not conduct or accept instructions via telephone.
We may conduct OTC business over electronic chat (such as telegram) where
these orders are logged via text.

\section{Market surveillance}
\crossref{VA-1: Question 47, 48, 49}
\crossref{Appendix F1: Part F (i)-(iv)}
\crossref{VA-2: Question 2.11(b)}

Our policies on market surveillance rely primarily on prevention, In
our token admission process, we will evaluate all tokens on the basis
of market liquidity and the potential for market manipulation or abuse
(see Token admission policy).

At the current time, all the tokens for which we plan to trade are
tokens for which there are substantial and liquid markets outside
our exchange and for which trading on our exchange will not have any
substantial price or market data, and hence the possibility of abusive
or manipulative trading through our exchange is low through the tokens
that we currently plan to trade.

Our token admission policies will not allow the exchange to trade any
tokens or products with limited liquidity, in which our exchange has a
large pricing impact, or tokens in which the exchange has a
proprietary interest without safeguards to insure against market abuse
or manipulation.  Should we at some point consider allowing the trading of
such tokens, we will develop specific policies to prevent abusive or
manipulative market trading, and communicate those policies with the
Securities and Futures Commission as these policies are under
development.

We will monitor the system for trades to identify any orders which are
intended to crash the system to attempt to exploit bugs or weaknesses
in the system, such as DDoS attacks or which otherwise could be considered an
attack on the integrity of the trading system.

Our trading engine will monitor the balances and transaction volumes
for each client.  If we detect behaviour that would
threaten the stability of the system, we would contact the client to
find the rationale for the trade and suspend trading if necessary to
protect the stability of the system.

\section{Trading rules}

\subsection{Conflict of interests}
\crossref{VA-1: Question 41}
\status{Fully implemented}
The firm itself will not invest in virtual assets or take proprietary
trading positions, will not be a counterparty to the trades, will not
conduct back-to-back traders and will not exchange in market making
trading of virtual assets.

The firm will allow staff and other associated market makers to
perform these activities, but these activities will be performed using
the personal capital of these entities and under the same terms as
other traders.

\subsection{No proprietary trading}
\crossref{VA-1: Question 1}
\status{Fully implemented}

The firm will not engage in proprietary trading on the exchange.  The firm will not use either operating funds or client funds for exchange
trading.  All liquidity operations will be done by outside
professional investors will not have any explicit or implicit claims
on the firm's balance sheet and will be responsible for their
profit and losses.

The auditor and responsible officers will be tasked with enforcing
this policy, and all staff will be made aware of the policy against
proprietary trading.

\subsection{No solicitation or recommendations}
\crossref{VA-1: Question 5}
\status{Fully implemented}
The firm will not recommend tokens or engage in solicitations for
tokens.  We do not have any plans to exchange any tokens, which would
be considered complex products.

\section{Incident reporting procedure}
\crossref{VA-1: Question 4}
\status{Compliance training materials to be developed and hotline to
  be set up}

Our incident reporting procedure consists of the routing reporting
process and hotline incident reporting.  All staff will be
made aware of these procedures.

\subsection{Compliance reporting}
\crossref{VA-1: Question 4(a)}
\status{Compliance training materials to be developed}

For reporting of (a) non-compliance with your licensing conditions or
any applicable law, regulations, codes, guidelines, circulars or
FAQs, etc. we will maintain an internal reporting mechanism and an
external reporting mechanism.

The firm will maintain an alternative reporting chain for
hotline/whistleblowing reporting.  There are two separate use cases.
The first is one in which the reporter believes that co-workers or
their immediate manager are operating in a non-compliant manner, but
they have confidence in senior management.  In this situation, the
company will maintain a hotline for compliance and will prepare
compliance training materials for internal compliance.

The firm will also maintain an outside tip line, by which staff can
report directly to senior management anonymously.

In situations, where staff do not have confidence in the ability of
senior management to deal with the situation, we will provide
compliance training materials outlining whistleblowing procedures by
which staff can contact the SFC directly and in our onboard materials
we will inform staff about whistleblowing and legal protections that
they have.

\subsection{Suspicious activity procedure}
\crossref{VA-1: Question 4(b)}
\status{Compliance training materials to be developed}

Staff will be trained to encourage a compliance culture with the
following process,
\begin{itemize}
  \item staff will be given compliance training as to how to identify
    and handle suspicious trading activity.  Staff will also be given
    compliance training concerning "anti-tipping" procedures and
    that any suspicious activity should not be raised with the client.
  \item in case, the staff believes that there is a compliance issue that
    can be addressed by senior management, then will be a hotline that
    will allow the staff to raise the issue with compliance.
  \item staff will also be given training on how to raise an issue
    with the financial regulators or law enforcement in case they
    believe that the issue cannot be resolved within the firm.  Staff
    will be given training as to their legal rights and obligations.
\end{itemize}

The firm will also maintain a robust client education procedure, by
which clients will be informed about the dangers of cryptocurrency and
fraudulent activity and about Hong Kong Police anti-fraud activities
through letters of no consent and Mareva injunctions.

\subsection{Technical incident reporting}
\crossref{VA-1: Question 4(c) and 4(d)}
\crossref{VATP Guidelines: Schedule 3}
\crossref{Appendix F1: Part H(xi)}
\label{label:techincident}
\status{Compliance training materials to be developed}
\status{Migrate technical reporting from GitHub to other platforms}

For routine reporting, the reports are to be made to the department
head, who will deliver reports to the responsible officer, who will
then serve as a single point of contact with the SFC.  This procedure
will be used in situations where there are (c) material failures or
interruptions of trading, accounting, clearing, or settlement systems
or (d) material issues identified by outside experts or consultants.

A technical incident report should be filed when the system
experiences a material delay or failure that renders it unusable by
clients.

\begin{itemize}
\item a clear explanation of the problem, including the root cause analysis;
\item the time of outage or delay;
\item the duration of outage or delay;
\item the platforms or systems affected during the outage or delay and subsequently;
\item whether this problem or a related problem has occurred before;
\item the number of clients affected at the time and the impact on these clients;
\item the steps taken to rectify the problem; and
\item steps taken to ensure that the problem does not occur again
\end{itemize}


\subsection{Cybersecurity incident reporting}
\crossref{VA-1: Question 52}
\crossref{VA-2: Section 2: Internal controls 2.2}
\crossref{Appendix F1: Part H (ix)}

We have not encountered any specific cybersecurity incident, although
our monitoring of firewalls has noted the hostile environment that
the system faces, as we have detected numerous attempts to break into our
system which are stopped at the firewall level.

The escalation procedure is that all cybersecurity incidents will be
reported directly to the head of the division and that compliance will
be notified of any incidents.  The technology division will immediately
take steps to mitigate the attack.  Reports will be given to
compliance, who will notify the regulators as necessary.

\subsection{Regulatory request process}
\label{label:regrequest}
In the event any staff receives a request for data purporting or
activity to come from a regulatory body, the staff member shall
immediately report the request to the compliance and the actual
request should be made by the administrative officer.

Staff should be alert to the possibility of spoofing and social
engineering, and shall hand off any regulatory requests to senior
management so that the senior management will verify the authenticity
of the request and take appropriate action to comply with the request.

\section{Staff policies}

\subsection{Communications}
All corporate communications will be done via corporate chat and
corporate e-mails.

\subsection{Staff general policies}

The firm maintains a policy of diversity and inclusion and a zero
tolerance policy toward harassment of any form.

The firm maintains a strict no-retaliation policy regarding bringing up
compliance issues.

\subsection{Staff screening}
\crossref{VA-2: Question 84}
We will perform standard due diligence checks against all persons with
access to client funds, including standard checks for criminal
background and behaviours involving breach of trust.

\subsection{Staff onboarding}

Staff should receive the following documents on onboarding:

\begin{itemize}
  \item Copy of policy manual with sections relevant to staff
    highlighted
\end{itemize}

\subsection{Staff trading}
\crossref{VA-2: Question 42}
\status{Fully implemented}

We encourage staff to trade on our systems in the belief that having
our staff use our products and services will improve them.
However, we will maintain the following principles and policies to
maintain protection with the wider financial community

\begin{itemize}
 \item Staff must provide a written statement as to the nature of
   their trading
  \item staff are only allowed to trade liquid tokens for which the
    firm does not maintain a proprietary interest
  \item orders by staff can only be executed using personal funds.
  \item Orders by staff will be made only through the standard trading
    interfaces.  Staff are strictly prohibited from given staff
    privileged trading over non-staff accounts.
  \item Staff must sign a waiver stating that in case of loss or
    liquidation of the company that all liabilities to staff will be
    paid out only when liabilities to other clients are paid out in
    full.  Staff must also sign a two-year "clawback" provision by
    which any profits made by personal trading are subject to
    "clawback" in case the firm folds
\end{itemize}

\subsection{Staff side businesses}
We encourage staff to have side businesses and other crypto-related
businesses.  However, staff must report any side businesses which may
create a conflict of interest to senior management.


\section{Data storage}
\subsection{Record keeping policy}
\crossref{VA-1: Question 100}
\crossref{VA-2: Question 2.10}
\crossref{Guidelines: Section XIV}
The firm shall keep the records required by the company under Section
XIV of the VASP guidelines.  This includes but is not limited:
\label{label:reckeep}

\begin{itemize}
  \item for a period of no less than seven years the financial data
    stated under Section XIV of the VASP Guidelines
  \item for not less than two years, order, transaction, and execution
    data stated under Section XIV of the VASP Guidelines, audit logs, and incident reports for all material system delays and failures
  \item for not less than two years or until the system ceases to be
    used, documentation on the design, development, development, and
    operation of the systems and documentation of the risk management
    controls of the trading system
\end{itemize}

The location of business records will be kept at the exchange's principal
place of business and will be kept in locked files with access
provided to the management and staff on a need-to-know basis.  These
records will be made available to the SFC upon request.  In case of a
request by the SFC or any other regulatory body, staff shall comply
with the request according to the regulatory request process in
section \ref{label:regrequest}

\subsection{Electronic Records Data Storage}
\crossref{VA1: Question 101}
All of our records will be backed up with a location in Hong Kong, and
a backup of all electronic records will be available at our place of business.
